Long groovy title goes here

### 2013-06-25 shanghai.tex
Added a \CSiso command

\newcommand{\cdef}[1]{{{\color{cyan}#1}\index{#1}}} 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-2pt\textbf{m},#1}}
\newcommand{\GN}[1]{\textswab{#1}}
\newcommand{\bGN}[1]{{\bar{\textswab{#1}}}}
\newcommand{\TT}{\underline{T}}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\cs}[1]{{\mathcal{#1}}}
\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
\newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
\newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}

@@

Character sheaves on $G$ form a category, denoted by $\CS(G)$. In
fact, $\CS(G)$ is a rigid symmetric monoidal category, so isomorphism
classes of character sheaves on $G$ form a group, denoted by
$\CS(G)_{/\text{iso}}$; this is the Picard group of the category of
character sheaves on $G$. Our application of character sheaves to
characters of algebraic tori over non-Archimedean local fields rests
on the Picard group of character sheaves on $G$, for certain smooth
group schemes $G$.

@@

The main result of this paper is a canonical isomorphism
\[
\CS(\textswab{T}_d)_{/\text{iso}} 
\iso
\Hom_{\leq d}(T(K),\EE^\times)
\] 
between the Picard group of the category of character sheaves on
$\textswab{T}_d$ and the group of characters $T(K) \to \EE^\times$ of
depth at most $d$.  Since these isomorphisms are compatible with
respect to $d$, we also .....  \Clifton{I'll come back to working on
  this when we're closer to being finished. I'd be just as happy if
  you took this cup from my lips, though.}  In particular, by
specializing to the case $T= \mathbb{G}_{\hskip-1pt\text{m},K}$ and by
choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
be), we arrive at a model for the group of quasi-characters of
$K^\times$: the monoidal category of character sheaves on the
Greenberg transform of the Neron model of
$\mathbb{G}_{\hskip-2pt\text{m},K}$.

@@

%\begin{proposition}\label{tensor}
The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal
category [insert reference] under
$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bar G})$ to
conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$
is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\CS(G)$ puts a group
structure on the set $\CS(G)_{/\text{iso}}$ of isomorphism classes in
$\CS(G)$; we refer to this as the \cdef{Picard group} of character
sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
\Clifton{Replace ncatlab with other references.}

@@

It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$
(pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$
if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
\[
\cdef{t_{G}} : \CS(G)_{/\text{iso}} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times),
\qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob_\cs{L},
\]
from the Picard group of character sheaves on $G$ to the character group of $G(\Fq)$.

@@

\begin{proposition}\label{prop:pullback}
  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
  $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes{\bar f})^*\mu,{\bar f}^*F)$
  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
  \[
  \xymatrix{
  \CS(G)_{/\text{iso}} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CS(H)_{/\text{iso}}\\
  \Hom_\text{grp}(G(\Fq),\EE^\times) \ar[r] & \Hom_\text{grp}(H(\Fq),\EE^\times)
  }
  \]
  is a commutative diagram of groups, where the lower homomorphism is
  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
\end{proposition}

@@

\begin{proposition}\label{prop:connected-1}
  If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then
  \[
  t_{G} : \CS(G)_{/\text{iso}} \to \Hom_\text{grp}(G(\Fq),\EE^\times),
  \]
  is an isomorphism of groups.
\end{proposition}

@@

  We have now shown that $b^* : \CS_0(G) \to \CS(G)$ is an equivalence
  of rigid monoidal categories. It follows immediately that $b^*$
  determines an isomorphism
  \[
  b^* : \CS_0(G)_{/\text{iso}} \mathop{\longrightarrow}^{\iso} \CS(G)_{/\text{iso}}
  \]
  of the Picard groups determined by these rigid monoidal categories.
  \Clifton{\textdbend This last sentence glosses over some subtle points;
    I might need to address them in the `two perspectives' section.}

  To finish the proof observe that the functions--sheaves dictionary,
  as it pertains to characters, shows that
  \[
  t_{G} : \CS_0(G)_{/\text{iso}}\to \Hom_\text{grp}(G(\Fq),\EE^\times)
  \]
  is an isomorphism of groups; see \cite{Laumon}*{1.1.3} or \cite{SGA4.5}*{Sommes trigonométriques}.
\end{proof}

@@

\begin{proposition}\label{prop:etale}
  If $G$ is a commutative \'etale group scheme over $\Fq$ and
  $G(\bFq)$ is finitely generated then there is a canonical
  isomorphism
  \[
  \CS(G)_{/\text{iso}} \longrightarrow H^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
  \qquad \text{given by}\qquad
  [\cs{L}] \mapsto [t_\cs{L}],
  \]
  where $t_\cs{L}: \Weil(\bFq/\Fq)\to \Hom_\text{grp}(G(\bFq),\EE^\times)$ is a cocycle such that
  \[
  \forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob_\cs{L}(g).
  \]
\end{proposition}

@@

  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$
    \Clifton{\textdbend There's hidden subtlety here too: maybe I
      should explain which Frobenius this is and how it acts. }
    such that
    \[
    \xymatrix{
      \gcs{L}_{\Frob(x)+\Frob(y)} \ar[d]_{F_{x+y}} \ar[rr]^{\mu_{\Frob(x),\Frob(y)}}
      &&\ar[d]^{F_x\otimes F_y}  \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)}\\
      \gcs{L}_{x+y} \ar[rr]^{\mu_{x,y}}
      && \gcs{L}_x \otimes\gcs{L}_y\\
      }
    \]
    commutes, for all $x,y\in G(\bFq)$.
  \end{enumerate}
  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
  character sheaves on $G$ corresponds to:
  \begin{enumerate}
  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
    of linear transformations (of one-dimensional $\EE$-vector spaces),
    as $x$ runs over $G(\bFq)$, such that
    \[
    \xymatrix{
      \ar[d]_{F_x} \gcs{L}_{\Frob(x)} \ar[r]^{\varphi_{\Frob(x)}} & \ar[d]^{F_x'} \gcs{L'}_{\Frob(x)}
      &\text{and}& \ar[d]_{\mu} \gcs{L}_{x+y} \ar[r]^{\varphi_{x+y}} & \ar[d]^{\mu'_{x+y}} \gcs{L'}_{x+y} \\
      \gcs{L}_x \ar[r]^{\varphi_x} & \gcs{L'}_x
      && \gcs{L}_x\otimes\gcs{L}_y \ar[r]^{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y\\
      }
    \]
    both commute.
  \end{enumerate}
  It is clear that the category defined by conditions \ref{cs.0},
  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
  \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the
  proposition by exhibiting an isomorphism between
  $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.

  To produce the isomorphism between $\CS(G(\bFq))_{/\text{iso}}$ and
  $H^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$. We
  will show that the group isomorphism does not depend on these
  choices.

@@

  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*)$
  factors through $\obj \CS(G(\bFq)) \to \CS(G(\bFq))_{/\text{iso}}$.
  To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
  let $t$ and $t'$ be any cocycles representing the classes in the
  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
  $t$ and $t'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EE^\times$
  by $\varphi_x(s(x)) = \phi(x) s'(x)$. By the second part of condition~\ref{cs.3},
  $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
  condition~\ref{cs.3}, $t'(\Frob) = t(\Frob) \cdot (\,^{\Frob^{-1}}\phi \cdot \phi^{-1})$,
  so $t$ and $t'$ are cohomologous. This concludes the definition of
  \begin{equation}\label{pich1}
    \CS(G(\bFq)_{/\text{iso}} \longrightarrow H^1(W_\Fq,G(\bFq)^*),
    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
  \end{equation}
  Now it follows from \eqref{t} that the image of the isomorphism
  class of $\cs{L}$ is indeed represented by a cocycle $t_\cs{L}$ such
  that $t_\cs{L}(\Frob) = t^\Frob_\cs{L}$ on $G(\Fq)$, which is to
  say, when evaluated at $\Frob$, the cocycle $t_\cs{L}$ is an
  extension of the trace of Frobenius of $\cs{L}$.

@@

%\input{snake}
\begin{theorem}\label{thm:snake}
  If $G$ is a smooth abelian group scheme, locally of finite type over
  $\Fq$, and the abelian group $\pi_0(G)(\bFq)$ (the geometric
  component group) is finitely generated, then the trace of Frobenius
  homomorphism
  \[
  t_{G} : \CS(G)_{/\text{iso}} \to \Hom(G(\Fq),\EE^\times),
  \]
  from the Picard group of the category of character sheaves on $G$ to
  the group of characters of $G(\Fq)$, is an isomorphism.
\end{theorem}

\begin{proof}
  Consider the short exact sequence in the category of smooth group
  schemes, locally of finite type over $\Fq$, defining the component
  group scheme for $G$:
  \begin{equation}\label{eq:pi0}
    \xymatrix{
      1 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
      }
  \end{equation}
  Let
  \[
  \xymatrix{
    & \ar[d] \ker t_{\pi_0(G)} & \ar@{.>}[d] \ker t_{G} & \ar[d] \ker t_{G^0} & \\
    0\ar[r] & \ar[d]^{t_{\pi_0(G)}} \CS(\pi_0(G))_{/\text{iso}} \ar[r]
    & \ar[d]^{t_{G}} \CS(G)_{/\text{iso}} \ar[r] & \ar[d]^{t_{G^0}} \CS(G^0)_{/\text{iso}} \ar[r] & 0\\
    0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EE^\times) \ar[r]
    & \ar@{.>}[d] \Hom(G(\Fq),\EE^\times) \ar[r] & \ar[d] \Hom(G^0(\Fq),\EE^\times) \ar[r] & 0\\
    & \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} & \\
    }
  \]
  be the commutative diagram of abelian groups obtained by applying
  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  By
  Proposition~\ref{prop:connected-1}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$.
  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$
  and $\coker t_{\pi_0(G)}=0$.

@@

  The sequence of Picard groups is right-exact: it is exact at
  $\CS(G^0)_{/\text{iso}}$ by Proposition~\ref{prop:restriction}; and
  it is exact at $\CS(G)_{/\text{iso}}$ because the left-square
  commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
  is exact at $\Hom(G(\Fq),\EE^\times)$ and $\coker t_{\pi_0(G)} =0$
  (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
  \[
  \image(\CS(\pi_0(G))_{/\text{iso}} \to \CS(G)_{/\text{iso}}) \subseteq \ker(\CS(G)_{/\text{iso}} \to \CS(G^0)_{/\text{iso}}),
  \]
  by the last part of Proposition~\ref{prop:pullback}. Specifically,
  suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on
  $G^0$. Then $t^\Frob_\cs{L}\vert_{G^0(\Fq)} = t^\Frob_{\cs{L}^0} =0$,
  by Proposition~\ref{prop:pullback} again. Since the sequence of
  character groups is exact at $\Hom(G(\Fq),\EE^\times)$, there is
  some $\chi \in \Hom(\pi_0(G)(\Fq),\EE^\times)$ such that the
  pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
  $t^\Frob_\cs{L}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
  there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
  to isomorphism, such that $t^\Frob_{\cs{L}_\chi} = \chi$. By
  Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the
  image of $\cs{L}_\chi$ under the monoidal functor $\CS(\pi_0(G)) \to \CS(G)$.

@@

%\input{application}
\begin{theorem}\label{thm:application}
  Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
  Picard group of the category of character sheaves on $\GN{T}_d$ is
  canonically isomorphic to the group of characters of $T(K)$ of depth
  less than $d$:
  \[
  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom_{< d}(T(K),\EE^\times).
  \]
\end{theorem}

>>>>

\newcommand{\cdef}[1]{{{\color{cyan}#1}\index{#1}}} 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-2pt\textbf{m},#1}}
\newcommand{\GN}[1]{\textswab{#1}}
\newcommand{\bGN}[1]{{\bar{\textswab{#1}}}}
\newcommand{\TT}{\underline{T}}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\cs}[1]{{\mathcal{#1}}}
\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
\newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
\newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
\newcommand{\CSbiso}[1]{\CS_0(#1)_{/\text{iso}}}
\newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}

@@

Character sheaves on $G$ form a category, denoted by $\CS(G)$. In
fact, $\CS(G)$ is a rigid symmetric monoidal category, so isomorphism
classes of character sheaves on $G$ form a group, denoted by
$\CSiso{G}$; this is the Picard group of the category of
character sheaves on $G$. Our application of character sheaves to
characters of algebraic tori over non-Archimedean local fields rests
on the Picard group of character sheaves on $G$, for certain smooth
group schemes $G$.

@@

The main result of this paper is a canonical isomorphism
\[
\CSiso{\textswab{T}_d} 
\iso
\Hom_{\leq d}(T(K),\EE^\times)
\] 
between the Picard group of the category of character sheaves on
$\textswab{T}_d$ and the group of characters $T(K) \to \EE^\times$ of
depth at most $d$.  Since these isomorphisms are compatible with
respect to $d$, we also .....  \Clifton{I'll come back to working on
  this when we're closer to being finished. I'd be just as happy if
  you took this cup from my lips, though.}  In particular, by
specializing to the case $T= \mathbb{G}_{\hskip-1pt\text{m},K}$ and by
choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
be), we arrive at a model for the group of quasi-characters of
$K^\times$: the monoidal category of character sheaves on the
Greenberg transform of the Neron model of
$\mathbb{G}_{\hskip-2pt\text{m},K}$.

@@

%\begin{proposition}\label{tensor}
The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal
category [insert reference] under
$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bar G})$ to
conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$
is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\CS(G)$ puts a group
structure on the set $\CSiso{G}$ of isomorphism classes in
$\CS(G)$; we refer to this as the \cdef{Picard group} of character
sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
\Clifton{Replace ncatlab with other references.}

@@

It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$
(pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$
if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
\[
\cdef{t_{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times),
\qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob_\cs{L},
\]
from the Picard group of character sheaves on $G$ to the character group of $G(\Fq)$.

@@

\begin{proposition}\label{prop:pullback}
  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
  $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes{\bar f})^*\mu,{\bar f}^*F)$
  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
  \[
  \xymatrix{
  \CSiso{G} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CSiso{H}\\
  \Hom_\text{grp}(G(\Fq),\EE^\times) \ar[r] & \Hom_\text{grp}(H(\Fq),\EE^\times)
  }
  \]
  is a commutative diagram of groups, where the lower homomorphism is
  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
\end{proposition}

@@

\begin{proposition}\label{prop:connected-1}
  If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then
  \[
  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EE^\times),
  \]
  is an isomorphism of groups.
\end{proposition}

@@

  We have now shown that $b^* : \CS_0(G) \to \CS(G)$ is an equivalence
  of rigid monoidal categories. It follows immediately that $b^*$
  determines an isomorphism
  \[
  b^* : \CSbiso{G} \mathop{\longrightarrow}^{\iso} \CSiso{G}
  \]
  of the Picard groups determined by these rigid monoidal categories.
  \Clifton{\textdbend This last sentence glosses over some subtle points;
    I might need to address them in the `two perspectives' section.}

  To finish the proof observe that the functions--sheaves dictionary,
  as it pertains to characters, shows that
  \[
  t_{G} : \CSbiso{G} \to \Hom_\text{grp}(G(\Fq),\EE^\times)
  \]
  is an isomorphism of groups; see \cite{Laumon}*{1.1.3} or \cite{SGA4.5}*{Sommes trigonométriques}.
\end{proof}

@@

\begin{proposition}\label{prop:etale}
  If $G$ is a commutative \'etale group scheme over $\Fq$ and
  $G(\bFq)$ is finitely generated then there is a canonical
  isomorphism
  \[
  \CSiso{G} \longrightarrow H^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
  \qquad \text{given by}\qquad
  [\cs{L}] \mapsto [t_\cs{L}],
  \]
  where $t_\cs{L}: \Weil(\bFq/\Fq)\to \Hom_\text{grp}(G(\bFq),\EE^\times)$ is a cocycle such that
  \[
  \forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob_\cs{L}(g).
  \]
\end{proposition}

@@

  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$
    \Clifton{\textdbend There's hidden subtlety here too: maybe I
      should explain which Frobenius this is and how it acts. }
    such that
    \[
    \xymatrix{
      \gcs{L}_{\Frob(x)+\Frob(y)} \ar[d]_{F_{x+y}} \ar[rr]^{\mu_{\Frob(x),\Frob(y)}}
      &&\ar[d]^{F_x\otimes F_y}  \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)}\\
      \gcs{L}_{x+y} \ar[rr]^{\mu_{x,y}}
      && \gcs{L}_x \otimes\gcs{L}_y\\
      }
    \]
    commutes, for all $x,y\in G(\bFq)$.
  \end{enumerate}
  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
  character sheaves on $G$ corresponds to:
  \begin{enumerate}
  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
    of linear transformations (of one-dimensional $\EE$-vector spaces),
    as $x$ runs over $G(\bFq)$, such that
    \[
    \xymatrix{
      \ar[d]_{F_x} \gcs{L}_{\Frob(x)} \ar[r]^{\varphi_{\Frob(x)}} & \ar[d]^{F_x'} \gcs{L'}_{\Frob(x)}
      &\text{and}& \ar[d]_{\mu} \gcs{L}_{x+y} \ar[r]^{\varphi_{x+y}} & \ar[d]^{\mu'_{x+y}} \gcs{L'}_{x+y} \\
      \gcs{L}_x \ar[r]^{\varphi_x} & \gcs{L'}_x
      && \gcs{L}_x\otimes\gcs{L}_y \ar[r]^{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y\\
      }
    \]
    both commute.
  \end{enumerate}
  It is clear that the category defined by conditions \ref{cs.0},
  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
  \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the
  proposition by exhibiting an isomorphism between
  $\CSiso{G(\bFq)}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.

  To produce the isomorphism between $\CSiso{G(\bFq)}$ and
  $H^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$. We
  will show that the group isomorphism does not depend on these
  choices.

@@

  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*)$
  factors through $\obj \CS(G(\bFq)) \to \CSiso{G(\bFq)}$.
  To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
  let $t$ and $t'$ be any cocycles representing the classes in the
  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
  $t$ and $t'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EE^\times$
  by $\varphi_x(s(x)) = \phi(x) s'(x)$. By the second part of condition~\ref{cs.3},
  $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
  condition~\ref{cs.3}, $t'(\Frob) = t(\Frob) \cdot (\,^{\Frob^{-1}}\phi \cdot \phi^{-1})$,
  so $t$ and $t'$ are cohomologous. This concludes the definition of
  \begin{equation}\label{pich1}
    \CSiso{G(\bFq} \longrightarrow H^1(W_\Fq,G(\bFq)^*),
    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
  \end{equation}
  Now it follows from \eqref{t} that the image of the isomorphism
  class of $\cs{L}$ is indeed represented by a cocycle $t_\cs{L}$ such
  that $t_\cs{L}(\Frob) = t^\Frob_\cs{L}$ on $G(\Fq)$, which is to
  say, when evaluated at $\Frob$, the cocycle $t_\cs{L}$ is an
  extension of the trace of Frobenius of $\cs{L}$.

@@

%\input{snake}
\begin{theorem}\label{thm:snake}
  If $G$ is a smooth abelian group scheme, locally of finite type over
  $\Fq$, and the abelian group $\pi_0(G)(\bFq)$ (the geometric
  component group) is finitely generated, then the trace of Frobenius
  homomorphism
  \[
  t_{G} : \CSiso{G} \to \Hom(G(\Fq),\EE^\times),
  \]
  from the Picard group of the category of character sheaves on $G$ to
  the group of characters of $G(\Fq)$, is an isomorphism.
\end{theorem}

\begin{proof}
  Consider the short exact sequence in the category of smooth group
  schemes, locally of finite type over $\Fq$, defining the component
  group scheme for $G$:
  \begin{equation}\label{eq:pi0}
    \xymatrix{
      1 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
      }
  \end{equation}
  Let
  \[
  \xymatrix{
    & \ar[d] \ker t_{\pi_0(G)} & \ar@{.>}[d] \ker t_{G} & \ar[d] \ker t_{G^0} & \\
    0\ar[r] & \ar[d]^{t_{\pi_0(G)}} \CSiso{\pi_0(G)} \ar[r]
    & \ar[d]^{t_{G}} \CSiso{G} \ar[r] & \ar[d]^{t_{G^0}} \CSiso{G^0} \ar[r] & 0\\
    0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EE^\times) \ar[r]
    & \ar@{.>}[d] \Hom(G(\Fq),\EE^\times) \ar[r] & \ar[d] \Hom(G^0(\Fq),\EE^\times) \ar[r] & 0\\
    & \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} & \\
    }
  \]
  be the commutative diagram of abelian groups obtained by applying
  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  By
  Proposition~\ref{prop:connected-1}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$.
  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$
  and $\coker t_{\pi_0(G)}=0$.

@@

  The sequence of Picard groups is right-exact: it is exact at
  $\CSiso{G^0}$ by Proposition~\ref{prop:restriction}; and
  it is exact at $\CSiso{G}$ because the left-square
  commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
  is exact at $\Hom(G(\Fq),\EE^\times)$ and $\coker t_{\pi_0(G)} =0$
  (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
  \[
  \image(\CSiso{\pi_0(G)} \to \CSiso{G}) \subseteq \ker(\CSiso{G} \to \CSiso{G^0}),
  \]
  by the last part of Proposition~\ref{prop:pullback}. Specifically,
  suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on
  $G^0$. Then $t^\Frob_\cs{L}\vert_{G^0(\Fq)} = t^\Frob_{\cs{L}^0} =0$,
  by Proposition~\ref{prop:pullback} again. Since the sequence of
  character groups is exact at $\Hom(G(\Fq),\EE^\times)$, there is
  some $\chi \in \Hom(\pi_0(G)(\Fq),\EE^\times)$ such that the
  pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
  $t^\Frob_\cs{L}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
  there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
  to isomorphism, such that $t^\Frob_{\cs{L}_\chi} = \chi$. By
  Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the
  image of $\cs{L}_\chi$ under the monoidal functor $\CS(\pi_0(G)) \to \CS(G)$.

@@

%\input{application}
\begin{theorem}\label{thm:application}
  Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
  Picard group of the category of character sheaves on $\GN{T}_d$ is
  canonically isomorphic to the group of characters of $T(K)$ of depth
  less than $d$:
  \[
  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EE^\times).
  \]
\end{theorem}

\begin{proof}
  By \ref{GNd} and \ref{fg}, we may apply Theorem~\ref{thm:snake} to
  $\GN{T}_d$ which provides a canonical isomorphism
  \[
  \CSiso{\GN{T}_d} \iso \Hom(\GN{T}_d(\Fq),\EE^\times).
  \]
  By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^d)$ canonically.
  To finish the proof we recall that the filtration of $T(K)$ used to
  define depth has the property that $\TT(\OK/\pK^d) \cong T(K) / T(K)_d$
  \cite[Prop 5.2]{Yu} for $d \in \ZZ_{>0}$.  Thus characters of $\GN{T}_d(\Fq)$ are
  in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
\end{proof}
